\PYGEOMETRY{}: a Python library for the creation of Monte Carlo radiation transport physical geometries

### 2020-09-14 public/paper/pyg4ometry.tex
spelling
spelling, ANRLR -> ANTLR

The core of \PYGEOMETRY{} consists of Python classes that mimic Geant4 solids, logical, physical volume objects, GDML parameters and material classes.
The constructors of the Python classes are kept as close to the original Geant4 C++ implementation so that \PYGEOMETRY{} users do not have to learn 
a new API. For example the \verb|G4Box| class in Geant4, has the XML tag \verb|Box| in GDML and is represented by the \pyinline{pyg4ometry.geant4.solid.Box} class in Python. The Python object constructor is kept a simialr to the Geant4 C++ constructor, but the length definitions are those used by GDML. For example, GDML uses full lengths whilst Geant4 uses half lengths. Geometry construction in Python proceeds in a way which is very similar to geometry construction in Geant4. A user relatively familiar with Geant4 should be able to start creating geometry in \PYGEOMETRY{} immediately. In the following sections novel or important developments in \PYGEOMETRY{} are described.

@@

%%%%%%%%%%%%%%%%%  Expression evaluation
In GDML symbolic expressions can be used to parametrise solids and their placement. These expressions are evaluated when the GDML is loaded into Geant4. 
In order to fully replicate the functionality of GDML an expression engine was implemented using ANTLR \cite{10.5555/2501720}. The GDML is loaded using 
standard XML modules and parsed using ANRLR to create an abstract syntax tree (AST).  GDML allows for the definition 
and assignment of variables. GDML expressions are not much more complicated than binary operators $+, -, \times, /$ and common trigonometric and special functions $\sin, \cos, \tan$ etc. The AST terminates on either expressions which evaluate to numbers or GDML variables. Internally, all \PYGEOMETRY{} 
classes use GDML expressions and not floating point numbers. Storing internal data as expressions allows for deferred evaluation (or re-evaluation) of 
solid parameters and  placements. This allows a user to update variables whilst defining geometry and the expression engine will update all internal values. 
An example of GDML expressions is shown in Listing~\ref{lst:gdmlExpressions}.

>>>>

The core of \PYGEOMETRY{} consists of Python classes that mimic Geant4 solids, logical, physical volume objects, GDML parameters and material classes.
The constructors of the Python classes are kept as close to the original Geant4 C++ implementation so that \PYGEOMETRY{} users do not have to learn 
a new API. For example the \verb|G4Box| class in Geant4, has the XML tag \verb|Box| in GDML and is represented by the \pyinline{pyg4ometry.geant4.solid.Box} class in Python. The Python object constructor is kept a similar to the Geant4 C++ constructor, but the length definitions are those used by GDML. For example, GDML uses full lengths whilst Geant4 uses half lengths. Geometry construction in Python proceeds in a way which is very similar to geometry construction in Geant4. A user relatively familiar with Geant4 should be able to start creating geometry in \PYGEOMETRY{} immediately. In the following sections novel or important developments in \PYGEOMETRY{} are described.

@@

%%%%%%%%%%%%%%%%%  Expression evaluation
In GDML symbolic expressions can be used to parametrise solids and their placement. These expressions are evaluated when the GDML is loaded into Geant4. 
In order to fully replicate the functionality of GDML an expression engine was implemented using ANTLR \cite{10.5555/2501720}. The GDML is loaded using 
standard XML modules and parsed using ANTLR to create an abstract syntax tree (AST).  GDML allows for the definition 
and assignment of variables. GDML expressions are not much more complicated than binary operators $+, -, \times, /$ and common trigonometric and special functions $\sin, \cos, \tan$ etc. The AST terminates on either expressions which evaluate to numbers or GDML variables. Internally, all \PYGEOMETRY{} 
classes use GDML expressions and not floating point numbers. Storing internal data as expressions allows for deferred evaluation (or re-evaluation) of 
solid parameters and  placements. This allows a user to update variables whilst defining geometry and the expression engine will update all internal values. 
An example of GDML expressions is shown in Listing~\ref{lst:gdmlExpressions}.
